Synergistic retrievals of ice in high clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-08-22 RST/Submission/RSTManuscript_rev2.tex
revision 2

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter, i.e. the normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  Based on the work of \cite{testud2001}, \cite{ferreira2001} and \cite{delanoe2014} showed that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
(where $a_{norm}$ and $b$ are constants) explains almost perfectly the relationships between IWC and Z calculated from observed PSDs.However, equation (\ref{eq:1}) is not  sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function  of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize $N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}. A scatter-plot analysis of relationships between the 2C-ICE IWC and the associated reflectivity suggests that the multiplicative coefficient in a power low ice-reflectivity relationship is parameterized as a function of temperature (or equivalently, as a function of height relative to the freezing level) in the default 2C-ICE retrievals. The default multiplicative coefficient (the value the provides the IWC estimate prior to the ingestion of the lidar observations) may be simply estimated by regressing the 2C-ICE IWC on the associated CloudSat reflectivity as a function of $H$, defined as height relative the freezing level. Specifically, a regression of the type $ln(IWC)=ln(a)+b*ln(Z)$ is performed for each bin referenced relative to the zero degree bin is performed, and the variation of $ln(a)$ is parameterized as a function of the relative height.  The results are shown in Figure \ref{f2}. As apparent in the figure, and as expected, $a$ exhibits a strong variation with the relative height. Given that any deviation of the multiplicative coefficient in an IWC-Z relation from an average is equivalent to a deviation of the associated $N_w$ from its mean value \citep{ferreira2001,delanoe2014}, the variation of $a$ as a function of relative-height may be converted into an $N_w$ as a function of relative-height relationship.  We, therefore, use the data in Figure \ref{f2} to parameterize $N_w$ as a function of the relative height.  Specifically, given that $(1-b)ln(N_w)+ln(a_{norm})=ln(a)$ and $ln(a)=ln(a_0)+s*H$, with $a_0$ and $s$ the intercept and the slope of a regression for the data in Figure \ref{f2}, we can express $N_w$ as a function of the relative height, slope $s$, and parameters $a_0$ and $a_{norm}$.

@@

The processing steps used to process the CS reflectivity observations and calculate the lidar, Ku-band and submillimeter-wave radiometer observations may be summarized as follows:
\begin{enumerate}
\item Derivation of physically consistent radar and radiometer lookup tables to relate basic radar and radiometer properties (e.g. reflectivity, attenuation, extinction, scattering-albedo, etc.) to PSD parameters such as $IWC$ and $D_m$. The tables are derived for a single of $N_w$, but are usable with any value of 
$N_w$ using the "normalization" operations described in \citep{grecu2011}.
\item Derivation of $N_w$-relative height parameterization using the 2C-ICE product.
\item Estimation of IWC and related PSD parameters from CS W-band radar observations, using the tables constructed Step 1, and $N_w$ profiles derived through parameterization obtained in Step 2 and perturbed using the random model described above. Specifically, given $N_w$ and the associated $Z$ at W-band, we estimate $IWC/N_w$ as a function of $Z/N_w$ using the normalized tables and then derive $IWC$ from $IWC/N_w$ and $N_w$.  A simple forward attenuation correction \citep{meneghini1978} is applied to the W-band reflectivity observations prior to the estimation of $IWC$.  Attenuation due to water vapor and other gases is calculated using the Rosenkranz model \citep{rosenkranz1998} assuming the same temperature, pressure and temperature profiles used in the radiometer simulations.

@@

The synergy of the instrument on the estimates may be investigated by simply incorporating lidar and radar observations into the retrieval process and comparing the results with the radiometer-only estimates.  Although the lidar observations are subject to attenuation, they are able to provide information about the vertical distribution of ice in clouds, mostly at the top of the clouds. The radar observations, on the other hand, are able to provide information in the bottom part of the clouds, where the lidar signal is below the noise level due to attenuation. Therefore, the combined used of lidar and radar observations is expected to provide a more complete characterization of the vertical distribution of ice in clouds and enable the derivation of more specific estimates than those derived from radiometer-only observations. It should be mentioned that, although deficiencies and potential biases in the simulated observations may distort conclusions to some degree, the forward models used in this study are state-of-the-art and are expected to enable a realistic characterization of the impact of individual instruments on the synergistic retrievals.

>>>>

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter, i.e. the normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  Based on the work of \cite{testud2001}, \cite{ferreira2001} and \cite{delanoe2014} showed that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
(where $a_{norm}$ and $b$ are constants) explains almost perfectly the relationships between IWC and Z calculated from observed PSDs.However, equation (\ref{eq:1}) is not  sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function  of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize $N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}. A scatter-plot analysis of relationships between the 2C-ICE IWC and the associated reflectivity suggests that the multiplicative coefficient in a power law ice-reflectivity relationship is parameterized as a function of temperature (or equivalently, as a function of height relative to the freezing level) in the default 2C-ICE retrievals. The default multiplicative coefficient (the value that provides the IWC estimate prior to the ingestion of the lidar observations) may be simply estimated by regressing the 2C-ICE IWC on the associated CloudSat reflectivity as a function of $H$, defined as height relative the freezing level. Specifically, a regression of the type $ln(IWC)=ln(a)+b*ln(Z)$ is performed for each bin referenced relative to the zero degree bin is performed, and the variation of $ln(a)$ is parameterized as a function of the relative height.  The results are shown in Figure \ref{f2}. As apparent in the figure, and as expected, $a$ exhibits a strong variation with the relative height. Given that any deviation of the multiplicative coefficient in an IWC-Z relation from an average is equivalent to a deviation of the associated $N_w$ from its mean value \citep{ferreira2001,delanoe2014}, the variation of $a$ as a function of relative-height may be converted into an $N_w$ as a function of relative-height relationship.  We, therefore, use the data in Figure \ref{f2} to parameterize $N_w$ as a function of the relative height.  Specifically, given that $(1-b)ln(N_w)+ln(a_{norm})=ln(a)$ and $ln(a)=ln(a_0)+s*H$, with $a_0$ and $s$ the intercept and the slope of a regression for the data in Figure \ref{f2}, we can express $N_w$ as a function of the relative height, slope $s$, and parameters $a_0$ and $a_{norm}$.

@@

The processing steps used to process the CS reflectivity observations and calculate the lidar, Ku-band and submillimeter-wave radiometer observations may be summarized as follows:
\begin{enumerate}
\item Derivation of physically consistent radar and radiometer lookup tables to relate basic radar and radiometer properties (e.g. reflectivity, attenuation, extinction, scattering-albedo, etc.) to PSD parameters such as $IWC$ and $D_m$. The tables are derived for a single value of $N_w$, but are usable with any value of $N_w$ using the "normalization" operations described in \citep{grecu2011}.
\item Derivation of $N_w$-relative height parameterization using the 2C-ICE product.
\item Estimation of IWC and related PSD parameters from CS W-band radar observations, using the tables constructed Step 1, and $N_w$ profiles derived through parameterization obtained in Step 2 and perturbed using the random model described above. Specifically, given $N_w$ and the associated $Z$ at W-band, we estimate $IWC/N_w$ as a function of $Z/N_w$ using the normalized tables and then derive $IWC$ from $IWC/N_w$ and $N_w$.  A simple forward attenuation correction \citep{meneghini1978} is applied to the W-band reflectivity observations prior to the estimation of $IWC$.  Attenuation due to water vapor and other gases is calculated using the Rosenkranz model \citep{rosenkranz1998} assuming the same temperature, pressure and temperature profiles used in the radiometer simulations.

@@

The synergy of the instrument on the estimates may be investigated by simply incorporating lidar and radar observations into the retrieval process and comparing the results with the radiometer-only estimates.  Although the lidar observations are subject to attenuation, they are able to provide information about the vertical distribution of ice in clouds, mostly at the top of the clouds. The radar observations, on the other hand, are able to provide information in the bottom part of the clouds, where the lidar signal is below the noise level due to attenuation. Therefore, the combined use of lidar and radar observations is expected to provide a more complete characterization of the vertical distribution of ice in clouds and enable the derivation of more specific estimates than those derived from radiometer-only observations. It should be mentioned that, although deficiencies and potential biases in the simulated observations may distort conclusions to some degree, the forward models used in this study are state-of-the-art and are expected to enable a realistic characterization of the impact of individual instruments on the synergistic retrievals.
